Karbowski model in 2-D

### 2020-01-24 paper/supplementary/supp.tex
Work on testing out the comp2 method again, after PNAS Rev 1 suggested this.
Adds an idea about divisive normalization

% Nice mathematics
\usepackage{amsmath}

@@

Taking inspiration from the divisive normalization idea in neural
networks~\cite{carandini_normalization_2011}, where the overall
activity of a group of neurons modulates the output response of an
individual member of the group, we will use the overall branching
level of all of the axons in a layer to modulate the response, $a_i'$,
of the branching level in each element.

The response can be written out with the normalization
equation~\cite{carandini_normalization_2011}:
%
\begin{equation}\label{eq:norm}
a_i' = h \; \frac {a_i^q} {\xi^q + \textstyle \sum_j^h a_{i,j}^q }
\end{equation}
%
in which $\xi$ and $q$ are free parameters and $n_e$ is the number of
hex elements in the domain of computation (although $n_e$ could also be
chosen as a free parameter if required). Here, I'll let $\xi=0$ and $q=1$.

$a_i'$, the `branching response', then has to be used to drive
connections, in practice, it is written back into $a_i$ on every
timestep.

@@

%
\begin{equation} \label{eq:dc_comp8}
\frac{\partial c_i}{\partial t} = -\alpha_i c_i
+ \beta_i n
[a_i]^k
\end{equation}
%
\begin{equation} \label{eq:da_comp8}
\frac{\partial a_i}{\partial t}
= \nabla\vcdot\mb{J}_i + \alpha_i c_i - \beta_i n [a_i]^k
\end{equation}
%
\begin{equation}\label{eq:norm_comp8}
a_i' = n_e \; \frac {a_i} {\textstyle \sum_j^{n_e} a_{i,j} }
\end{equation}
%
($a_i'$ becomes $a_i$ in the next computational step.)
%
\begin{equation} \label{eq:conserve_NM_comp8}
n = 1 - \sum_{i=1}^{N} c_i
\end{equation}
%
\begin{equation} \label{eq:divJExpanded_comp8}
\nabla\vcdot\mb{J}_i(\mb{x}) =
D \dvrg a_i - a_i\nabla\vcdot\mb{g} - \mb{g}\vcdot\nabla a_i
\end{equation}

@@

An idea to get around this is to introduce an additional multiplier to
the normalization, which is the mean initial branching density per
element, $d_i/n_e$, so that Eq.~\ref{eq:norm_comp8} becomes

\begin{equation}\label{eq:norm_comp8plus}
a_i' = d_i \; \frac {a_i} {\textstyle \sum_j^{n_e} a_{i,j} }
\end{equation}

>>>>

% Nice mathematics
\usepackage{amsmath}
\usepackage{esint}

@@

Taking inspiration from the divisive normalization idea in neural
networks~\cite{carandini_normalization_2011}, where the overall activity of a
group of neurons modulates the output response of an individual member of the
group, we will use the overall branching level of all of the axons in a layer
to modulate the response, $a_i[j]'$, of the branching level in each element
$j$ (using this notation ($a_i[j]$) makes explicit that we're talking about a
system containing $n_e$ discrete elements indexed by $j$).

The response can be written out with the normalization
equation~\cite{carandini_normalization_2011}:
%
\begin{equation}\label{eq:norm}
a_i[j]' = h \; \frac {(a_i[j])^q} {\xi^q + \textstyle \sum_j^h (a_{i}[j])^q }
\end{equation}
%
in which $\xi$ and $q$ are free parameters and $n_e$ is the number of
hex elements in the domain of computation (although $n_e$ could also be
chosen as a free parameter if required). Here, I'll let $\xi=0$ and $q=1$.

$a_i[j]'$, the `branching response' at element $j$, then has to be used to
drive connections, in practice, it is written back into $a_i[j]$ on every
timestep.

@@

%
\begin{equation} \label{eq:dc_comp8}
\frac{\partial c_i}{\partial t} = -\alpha_i c_i
+ \beta_i n
[a_i]^k
\end{equation}
%
\begin{equation} \label{eq:da_comp8}
\frac{\partial a_i}{\partial t}
= \nabla\vcdot\mb{J}_i + \alpha_i c_i - \beta_i n [a_i]^k
\end{equation}
%
\begin{equation}\label{eq:norm_comp8}
a_i[j]' = n_e \; \frac {a_i[j]} {\textstyle \sum_j^{n_e} a_i[j] }
\end{equation}
%
($a_i'$ becomes $a_i$ in the next computational step.)
%
\begin{equation} \label{eq:conserve_NM_comp8}
n = 1 - \sum_{i=1}^{N} c_i
\end{equation}
%
\begin{equation} \label{eq:divJExpanded_comp8}
\nabla\vcdot\mb{J}_i(\mb{x}) =
D \dvrg a_i - a_i\nabla\vcdot\mb{g} - \mb{g}\vcdot\nabla a_i
\end{equation}

@@

An idea to get around this is to introduce an additional multiplier to
the normalization, which is the mean initial branching density per
element, $d_i/n_e$, so that Eq.~\ref{eq:norm_comp8} becomes
%
\begin{equation}\label{eq:norm_comp8plus}
a_i[j]' = d_i \; \frac {a_i[j]} {\textstyle \sum_j^{n_e} a_i[j] }
\end{equation}
%
which is (making time explicit now):
%
\begin{equation}\label{eq:norm_comp8plus1}
        a_i[j](t)' = \sum_j^{n_e} a_i[j](0) \; \frac {a_i[j](t)} {\textstyle \sum_j^{n_e} a_i[j](t) }
\end{equation}

One further extension is to note that in the K\&E simulation, the quantity of
axon branching in the system is bounded and the number of connections and
branching quantity is related. So we could normalize the `proportion of $a_i$
which is not participating in connections'.
%
\begin{equation}\label{eq:norm_comp8plus2}
        a_i[j](t)' = \sum_j^{n_e} \big[ a_i[j](0) - c_i[j](t) \big] \; \frac {a_i[j](t)} {\textstyle \sum_j^{n_e} a_i[j](t) }
\end{equation}
%
The continuous equivalent, if the surface is called $S$, would be:
%
\begin{equation} \label{eq:norm_comp8plus3}
  a_i(\mathbf{x}, t) = \oiint_{S} \big[  a_i(\mathbf{x}, 0) - c_i(\mathbf{x},
  t) \big]  dS \; \frac {a'_i(\mathbf{x}, t)} {\oiint_{S}
  a'_i(\mathbf{x}, t) dS}
\end{equation}
